Ae. albopictus CPP manuscript

### 2020-01-31 GDDdata_input.Rmd
lab meeting

```
```{r}
gdd400_jp <- read.csv("GDD400_JP.csv", check.names=FALSE) %>% gather(year, gdd400, "1998":"2018", factor_key=FALSE)
gdd400_jp$year<-as.numeric(gdd400_jp$year)
ggplot(gdd400_jp, aes(x=year, y=gdd400, color=pop)) + geom_point() + geom_line() + geom_vline(xintercept=c(2008,2018))

@@

>>>>

```
```{r}
gdd400_jp <- read.csv("GDD400_JP.csv", check.names=FALSE) %>% gather(year, gdd400, "1998":"2018", factor_key=FALSE)
gdd400_jp$year<-as.numeric(gdd400_jp$year)

@@

```{r}
#model comparison of gdd-cpp relationship, with and without country as factor
data_18<-filter(gdd400_all_new, year==2007, CPP_YEAR==2018)
model1<-lm(Estimate~gdd400, data=data_18)
model2<-lm(Estimate~gdd400*country, data=data_18)
anova(model1, model2)

model3<-lm(Estimate~latitude, data=data_18)
model4<-lm(Estimate~latitude*country, data=data_18)
anova(model3, model4)
```

### 2020-01-31 MS.Rmd
lab meeting

```{r fig.cap="Figure 2B: Diapause incidence by country and year. Lines represent locally estimated scatterplot smoothing (LOESS). Solid lines, 2018 data; dotted lines, 2008 data.", echo=FALSE, message=FALSE}
#country_DI
country_DI_color<-ggplot(filter(DI_short_2, year!=1988), aes(x=lat, y=DI, color=country, shape=year)) + scale_color_manual(values=c("red","blue")) + geom_point(size=3) + theme_bw() + theme(legend.position=c(0.9,0.3)) + stat_smooth(aes(linetype=year), se=FALSE) + scale_linetype_manual(values=c("dotted","solid")) + xlab("Latitude") + ylab("Short-day diapause incidence")

@@

@@

>>>>

```{r fig.cap="Figure 2B: Diapause incidence by country and year. Lines represent locally estimated scatterplot smoothing (LOESS). Solid lines, 2018 data; dotted lines, 2008 data.", echo=FALSE, message=FALSE}
#country_DI

country_DI_color<-ggplot(filter(DI_short_2, year!=1988), aes(x=lat, y=DI, color=country, shape=year)) + scale_color_manual(values=c("red","blue")) + geom_point(size=3) + theme_bw() + theme(legend.position=c(0.9,0.3)) + stat_smooth(aes(linetype=year), se=FALSE) + scale_linetype_manual(values=c("dotted","solid")) + xlab("Latitude") + ylab("Short-day diapause incidence")

@@

ggplot(filter(DI_short_2, year!=1988), aes(x=lat, y=DI, color=country, shape=year)) + scale_color_manual(values=c("red","blue")) + geom_point(size=3) + theme_bw() + theme(legend.position=c(0.9,0.3)) + stat_smooth(aes(linetype=year), se=FALSE) + scale_linetype_manual(values=c("dotted","solid")) + xlab("Latitude") + ylab("Short-day diapause incidence")

ggplot(filter(DI_short_2, year!=1988), aes(x=lat, y=DI, fill=country, shape=year)) + scale_fill_manual(values=c("black","gray")) + 
scale_shape_manual(values=c(21,24)) + geom_point(size=3) + theme_bw() + theme(legend.position=c(0.9,0.3)) + stat_smooth(aes(linetype=year, color=country), se=FALSE) + scale_color_manual(values=c("black","gray")) + scale_linetype_manual(values=c("dotted","solid")) + xlab("Latitude") + ylab("Short-day diapause incidence")

@@

```{r}
#Dose response curve plot from Jen
#cpp<-read.table("CPP.csv", header=TRUE, sep=",")
#cpp

#fm1<-cbind(hatched, nothatched)~photoperiod
#cppmodel<-glm(fm1, data=cpp, family=binomial())

#summary(cppmodel)

#fitteddata1<-predict(cppmodel,type="response")
#fitteddata1

#plot(cpp$photoperiod, fitteddata1, ylab="Probability of hatching",
 #    xlab="photoperiod", ylim=c(0,1))
  #   lines(cpp$photoperiod,fitteddata1, lty=1)
#y<-cpp$hatched/(cpp$hatched+cpp$nothatched)
#text(cpp$photoperiod,y)
#hours<-(cppmodel$coefficients["(Intercept)"])/cppmodel$coefficients["photoperiod"]
#hours
